### 2017-03-18 titlepage.tex
Bump years, date, and ordinal conference number for 2017
My God, this could use some automation!

\textsc{\Large a record of the proceedings of}\\[0.5cm]
% Title
\HRule \\[0.4cm]
{ \Huge \sf SIGBOVIK 2016 \\[0.4cm] }

@@

the tenth annual intercalary robot dance party in celebration

@@

% Bottom of the page
{\Large carnegie mellon university\\[0.25cm]
pittsburgh{\fontspec{Birbaslo.ttf} ,} pa\\[0.3cm]
april $1${\fontspec{Birbaslo.ttf} ,} $2016$}

>>>>

\textsc{\Large a record of the proceedings of}\\[0.5cm]
% Title
\HRule \\[0.4cm]
% TODO: Don't listen to copyright-page.tex: this also needs to be updated every year!
{ \Huge \sf SIGBOVIK 2017 \\[0.4cm] }

@@

% TODO: So does this!
the eleventh annual intercalary robot dance party in celebration

@@

% Bottom of the page
{\Large carnegie mellon university\\[0.25cm]
pittsburgh{\fontspec{Birbaslo.ttf} ,} pa\\[0.3cm]
% TODO: And this one!
april $1${\fontspec{Birbaslo.ttf} ,} $2017$}
